What We Eval in the Shadows

### 2021-08-12 paper/main.tex
Update 6.dsl

\paragraph{Domain-Specific Language}
A domain-specific language leverages R's grammar but redefines it semantics in
some suitable way. The usage example illustrates string interpolation. The
\k{glue} function extracts snippets of code enclosed between braces and
evaluates them using \eval, and finally splices their results to construct the
result.

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{glue::glue}:}
\begin{lstlisting}
 library(glue)
 greeting <- "Hello"
 glue('{greeting} World!')
 #> Hello World!
\end{lstlisting}\medskip
\end{minipage}

>>>>

\paragraph{Domain-Specific Language}
A domain-specific language leverages R's grammar but redefines it semantics in
some suitable way. The usage example illustrates string interpolation. The
\k{glue} function from the \k{glue} package extracts snippets of code enclosed
between braces and evaluates them using \eval, and finally splices their
results to construct the result.

\begin{minipage}{.95\textwidth}
\medskip
\begin{lstlisting}
> greeting <- "Hello"
> glue('{greeting} World!') 
# Hello World!
\end{lstlisting}\medskip
\end{minipage}
